Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-11-13 paper/meg_exps.tex
fix

\begin{wrapfigure}{r}{.5\textwidth}
  \vspace{-11ex}
  \begin{center}
    \includegraphics[width=0.48\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg.pdf}

    \label{fig:meg_results}
  \end{center}
  \caption{Multiple models (color-coded) are compared on their ability to reliably predict single-trial MEG signals evoked by words. Left. Average improvement of correlation coefficient $\Delta R$ for each of the four features (rows). Error bars indicate standard error of the mean (SEM) across subjects. Right. Average $\Delta R$ across time for each subject (dots). Top horizontal lines indicate when B2B significantly outperforms other methods (red) and vice versa.}
  \vspace{-6ex}
\end{wrapfigure}

@@

>>>>

@@

\begin{wrapfigure}{r}{.6\textwidth}
  \vspace{-12ex}
  \begin{center}
    \includegraphics[width=0.6\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg.pdf}
  \end{center}
  \vspace{-5ex}
  \caption{Multiple models (color-coded) are compared on their ability to reliably predict single-trial MEG signals evoked by words. Left. Average improvement of correlation coefficient $\Delta R$ for each of the four features (rows). Error bars indicate standard error of the mean (SEM) across subjects. Right. Average $\Delta R$ across time for each subject (dots). Top horizontal lines indicate when B2B significantly outperforms other methods (red) and vice versa. \label{fig:meg_results}
}
\end{wrapfigure}
